¥section{Methodology}
¥label{sec:method}

We employ a three-pronged computational approach: (1) physics-based battery simulation to model impurity effects on CE, (2) analysis of published SEI composition data to ground our findings in experiment, and (3) dose-response modeling to predict optimal impurity concentrations. We describe each component below.

¥subsection{Physics-Based Simulation}
¥label{sec:simulation}

¥para{Battery model.}
We use the Single Particle Model with electrolyte (SPMe) implemented in ¥pybamm v26.3.0‾¥citep{pybamm2020} with the SEI growth submodel. The SPMe captures solid-phase diffusion, electrolyte transport, and electrochemical kinetics while remaining computationally efficient. We adopt the Chen 2020 parameterization for an NMC/graphite pouch cell‾¥citep{chen2020parameterization}, which provides experimentally validated values for all geometric, transport, and kinetic parameters.

¥para{Impurity parameterization.}
We model impurity effects by modifying three key SEI parameters, guided by the physical mechanisms reported in the literature:

¥begin{itemize}[leftmargin=*,itemsep=2pt,topsep=2pt]
    ¥item ¥textbf{SEI kinetic rate constant} ($k_¥text{SEI}$): Controls the rate of SEI-forming side reactions. Catalytic impurities (e.g., Fe) increase this parameter.
    ¥item ¥textbf{SEI resistivity} ($¥rho_¥text{SEI}$): Determines the ionic resistance through the SEI layer. Compact inorganic SEI (promoted by Mg and O$_2$ species) reduces this parameter.
    ¥item ¥textbf{Exchange current density} ($j_0$): Governs the main electrochemical reaction rate. Impurities can enhance or inhibit lithium intercalation kinetics.
¥end{itemize}

¥Tabref{tab:parameterization} summarizes the literature-based parameterization for each impurity type. We apply multiplicative scaling factors relative to the baseline (ultra-pure) parameters, with scaling magnitude proportional to impurity concentration.

¥begin{table}[t]
    ¥centering
    ¥caption{Impurity parameterization for ¥pybamm simulations. Arrows indicate direction of parameter modification relative to the ultra-pure baseline. Scaling magnitudes are derived from experimental observations in ¥citet{choe2024reevaluation}, ¥citet{fink2021metallic}, and ¥citet{baakes2023impact}.}
    ¥begin{tabular}{@{}lccc@{}}
        ¥toprule
        Impurity & $k_¥text{SEI}$ & $¥rho_¥text{SEI}$ & $j_0$ ¥¥
        ¥midrule
        Mg      & $¥uparrow$ (slight) & $¥downarrow$ & $¥uparrow$ (slight) ¥¥
        H$_2$O  & $¥uparrow$ & $¥downarrow$ then $¥uparrow$ & $¥downarrow$ ¥¥
        Fe      & $¥uparrow¥uparrow$ & $¥uparrow$ & $¥downarrow$ ¥¥
        O$_2$ species & $¥uparrow$ (slight) & $¥downarrow$ & $¥approx$ ¥¥
        ¥bottomrule
    ¥end{tabular}
    ¥label{tab:parameterization}
¥end{table}

¥para{Cycling protocol.}
All simulations follow the same protocol: constant-current constant-voltage (CC-CV) charge at 1C to 4.2‾V with a C/50 cutoff, followed by constant-current discharge at 1C to 2.5‾V, with 5-minute rest periods between half-cycles. We simulate 100 cycles per scenario (50 cycles for fine-grained dose sweeps in Experiment‾3). Formation cycles (1--9) are excluded from analysis to focus on steady-state behavior.

¥para{Scenarios.}
We simulate 13 scenarios in Experiment‾1: one ultra-pure baseline and four impurity types at three concentrations each (50, 200, and 1{,}000‾¥ppm). In Experiment‾3, we extend to finer concentration sweeps using combined simulation and literature data.

¥subsection{SEI Composition Analysis}
¥label{sec:sei_analysis}

We analyze the publicly available Baakes et al.¥ KITopen dataset (DOI:10.35097/1804), which contains thermal abuse modeling data for seven SEI conditions (organic SEI, wet electrode, thin SEI, dry electrode, reference, inorganic SEI, and thick SEI) with $>10{,}000$ time points each. We extract self-heating onset temperatures and time-to-runaway for each condition, and track species evolution (LiF, Li$_2$CO$_3$, LEDC, LiOH, H$_2$O, PF$_5$) during thermal abuse. This analysis connects SEI composition to stability and validates that impurities promoting inorganic SEI improve both CE and safety.

¥subsection{Dose-Response Modeling}
¥label{sec:dose_response}

We fit two mechanistic dose-response models to the combined simulation and literature data:

¥para{Hormesis model.}
For impurities exhibiting beneficial-then-detrimental behavior (Mg, O$_2$ species), we use:
¥begin{equation}
    ¥text{CE}(c) = ¥text{CE}_¥text{base} + A ¥cdot c ¥cdot ¥exp¥left(-c / c_¥text{opt}¥right),
    ¥label{eq:hormesis}
¥end{equation}
where $c$ is impurity concentration, $A$ controls the effect magnitude, and $c_¥text{opt}$ is the concentration at peak benefit.

¥para{Monotonic detrimental model.}
For universally harmful impurities (H$_2$O, Fe), we use:
¥begin{equation}
    ¥text{CE}(c) = ¥text{CE}_¥text{base} - k ¥cdot ¥left(c / 1000¥right)^n,
    ¥label{eq:monotonic}
¥end{equation}
where $k$ and $n$ are fitted parameters controlling the rate and shape of degradation. Model parameters are fitted using nonlinear least squares (SciPy v1.17.1).

¥subsection{Evaluation Metrics}
¥label{sec:metrics}

We evaluate impurity effects using four metrics:

¥begin{itemize}[leftmargin=*,itemsep=2pt,topsep=2pt]
    ¥item ¥textbf{Mean CE}: Average $Q_¥text{discharge}/Q_¥text{charge} ¥times 100¥%$ over cycles 10--100.
    ¥item ¥textbf{CE stability} ($¥sigma_¥text{CE}$): Standard deviation of CE over cycles 10--100.
    ¥item ¥textbf{Capacity retention}: $Q_¥text{cycle¥,100} / Q_¥text{cycle¥,10} ¥times 100¥%$.
    ¥item ¥textbf{SEI-related Li loss}: Total lithium consumed by SEI side reactions.
¥end{itemize}

¥subsection{Statistical Analysis}
¥label{sec:stats}

We apply Welch's $t$-tests for pairwise comparisons between each impurity scenario and the baseline, with significance at $¥alpha=0.05$. We use one-way ANOVA to test for differences across impurity types. Pearson correlation quantifies the relationship between SEI resistivity and capacity retention. All tests use SciPy v1.17.1.
